# Task 1: Create a Custom S3 Class

-   Define a custom S3 class called "Circle" that represents a circle. The class should store the radius of the circle.
-   Write a constructor function Circle() that takes the radius as input and assigns the class "Circle" to the object.
-   Write a print.Circle() method to display the radius and area of the circle when the object is printed. Use the formula for the area of a circle: area = π \* radius\^2.

```{r} 
Circle1 <- function(radius) {
  # Create a list to represent the Circle object
  obj <- list(radius = radius)
  
  # Set the class of the object to "Circle"
  class(obj) <- "Circle1"
  
  return(obj)
}

print.Circle1 <- function(x) {
  cat("The radius is\n")
  print(x$radius)
  cat("\nThe area is:\n")
  print(x$radius^2*pi)
}

circle = Circle1(5)
print(circle)
```
# Task 2: Define a Custom Operator
- Define a custom operator %>% that calculates the distance between the centers of two circles and checks if they intersect. The operator should return TRUE if the circles intersect and FALSE otherwise. The formula for the distance between two circles is: distance = sqrt((x2 - x1)^2 + (y2 - y1)^2).
- Assume that the circles are centered at (x1, y1) and (x2, y2), respectively.
- Two circles intersect if the distance between their centers is less than or equal to the sum of their radii.
- Modify the Circle class to include x and y coordinates for the center of the circle.
```{r}
Circle <- function(radius, x, y){
  
  obj <- list(radius = radius, x=x, y=y)
  
  class(obj) <- "Circle"
  
  return (obj)
}

# Define custom addition operator for MyVector
`%>%` <- function(a, b) {
  if (!inherits(a, "Circle") || !inherits(b, "Circle")) {
    stop("Both operands must be of class 'Circle'.")
  }
  distance <- sqrt((b$x - a$x)^2 + (a$y - b$y)^2)
  
  result <- distance <= (a$radius + b$radius)
  print(result)  # This prints only once
}



circle1 <- Circle(radius = 3, x = 0, y = 0)
circle2 <- Circle(radius = 4, x = 5, y = 0)
circle1 %>% circle2
```
Task 3: Write a Function for the Class
Write a function circumference() that calculates the circumference of a Circle object. The formula for the circumference is: circumference = 2 * π * radius.

Add this function as a method for the Circle class so that it can be called directly on objects of the class.

```{r}
circumference <- function(x) {
  if (!inherits(x, "Circle1")){
    stop("Not a circle")
  }
  result = x$radius^2*pi
  
  return (result)
}

circle1 = Circle1(5)
circumference(circle1)
```
Task 4: Create a Custom S4 Class
Define a custom S4 class called "Rectangle" that represents a rectangle. The class should store the length and width of the rectangle.

Write a constructor function Rectangle() that takes the length and width as input and creates an object of the "Rectangle" class.

Write a show() method for the Rectangle class to display the length, width, and area of the rectangle when the object is printed.

```{r}
library(methods)

setClass("Rectangle",
  slots = list(
    length = "numeric",
    width = "numeric"
  )
)

# Constructor for Rectangle
Rectangle <- function(length, width) {
    if (!is.numeric(length) || !is.numeric(width)) {
    stop("Invalid input types")
  }

  new("Rectangle", length = length, width = width)
}

# Print method for Rectangle
setMethod("show", "Rectangle", function(object) {
  cat("Rectangle object:\n")
  cat("Length is", object@length, "\n")
  cat("Width is", object@width, "\n")
  cat("Area is", object@length*object@width)
})

setGeneric("test", function(object) {
  standardGeneric("test")  # A placeholder function that will be dispatched to the right method
})

setMethod("test", "Rectangle", function(object){
  print("random test")""
})

rect = Rectangle(3,6)
show(rect)
test(rect)

```
Task 5: Define a Custom Operator for the S4 Class
Define a custom operator %==% that compares two Rectangle objects and checks if they have the same area.

The operator should return TRUE if the areas are equal and FALSE otherwise.

```{r}
"%==%" <- function(a,b) {
  if (!inherits(a, "Rectangle") || !inherits(b, "Rectangle")) {
    stop("Both operands must be of class 'Circle'.")
  }
  a@length * a@width == b@length * b@width
}

rectangle1 <- Rectangle(length = 4, width = 6)
rectangle2 <- Rectangle(length = 3, width = 8)
rectangle1 %==% rectangle2

```